Towards a Neural Co-Processor Which Restores Movement After Stroke: Modeling a Proof-of-Concept

### 2021-09-25 paper/article.tex
Paper with complete abstract

\begin{abstract}
Brain co-processors\cite{rao.coproc} are devices which use artificial intelligence (AI) and closed-loop
neurostimulation to shape neural activity and to bridge injured neural circuits for
targeted repair and rehabilitation.
\end{abstract}

@@

Closed-loop control:
\begin{itemize}
	\item \cite{walker.inception} Inception Loops: driving brain states
	\item \cite{kahana.biomarker} “Closed loop” here refers to when to apply stimulation, always of the same type and at the same site, based on memory performance.
	\item \cite{tafazoli.acls} ACLS
\end{itemize}

@@

\section{Method}
asdf

\section{Results}
asdf

\section{Discussion}
asdf

@@

\section{Acknowledgements}
asdf

>>>>

\begin{abstract}
\textit{Objective} Brain co-processors\cite{rao.coproc} are devices which use artificial
intelligence (AI) and closed-loop neurostimulation to shape neural activity and to bridge
injured neural circuits for targeted repair and rehabilitation. The co-processor framework
offers a flexible approach to learning stimulation policies that optimize for
(a) specific regimes of neural activities, or (b) external task performance.
For example, it may seek to learn a complex stimulation policy, to aid a
stroke victim in reaching to grasp an object.
Through the use of artificial neural networks (ANNs) and deep learning, the
co-processor co-adapts with the neural circuit, allowing it to seek optimal
stimulation policies, and adapt them as the neural circuit changes. The results
presented here demonstrate a neural co-processor for the first time through
the use of a simulation, and explore some of the core algorithms that may allow them
to succeed. \textit{Approach} We provide the first proof-of-concept of a neural
co-processor, through the use of a simulated neural circuit, based on (ANNs).
The simulated circuit performs a reach-to-grasp task, based on visual
input which is designed to closely resemble a similar circuit in a primate brain
\cite{michaels.mrnn}. We simulate a variety of lesions by altering the model, and
then demonstrate a co-processor's ability to restore lost function through
``stimulation'' of that model. We further test the ability of a
co-processor to adapt its stimulation as the simulated brain
undergoes changes. \textit{Main results} Our simulated co-processor
successfully co-adapts with the neural circuit to accomplish the external reaching
task. The co-processor framework demonstrated here adapts to a variety of lesion
types, and to ongoing changes in the simulated brain. \textit{Significance} The proof-of-concept here
outlines a co-processor model, as well as our approach to training it, leading to
insights on how such a model may be developed for \textit{in vivo} use. We believe this
co-processor design will allow for learning complex stimulation policies that
help restore function to a stroke victim. This initial proof-of-concept lays
the foundation for a future demonstration \textit{in vivo}.
\end{abstract}

@@

* Introduce the notion of a co-processor

* BCIs: a single direction
* Increasingly sophisticated ML techniques applied to decoding
** See 2019Raj
* Encoding models, stimulation models (cite)

* Bi-directional BCIs (BBCIs)
** Closed loop control
\begin{itemize}
	\item \cite{walker.inception} Inception Loops: driving brain states
	\item \cite{kahana.biomarker} “Closed loop” here refers to when to apply stimulation, always of the same type and at the same site, based on memory performance.
	\item \cite{tafazoli.acls} ACLS
\end{itemize}

Need for more complex stimulation policies, and need for optimizing task performance.

Demonstration by way of simulation.

@@

\section{Method}

* Overview of test bed
** Michaels model
** Lesion designs
** Stimulation design

* EN architecture
* CPN architecture

\section{Results}

* Task performance improves drastically
* Fine tuning takes a long time
* Object classes separate
* Can co-adapt with the brain, as it changes

* White noise and noised params
** Learning instability
** Predictive power isn't enough

\section{Discussion}
* Training efficiency
* Spectrum from simple low dimensional stimulation vectors today to higher dimensional future
* Toward in vivo application

@@

\section{Acknowledgements}
Ganguly, Priya, Anca, Justin, Luciano
